Summary Statistics

### 2025-02-27 extensive_tests/draft-sumstat-vignette.Rmd
Updating summary statistics with finished meanSiteFChange_cherry

```{r}
# Set example tree and methylation data
tree <- "((a:1.5,b:1.5):2,(c:2,d:2):1.5);"
data <- list(
    list(rep(1,10), rep(0,5), rep(1,8)), # tip a
    list(rep(1,10), rep(0.5,5), rep(0,8)), # tip b
    list(rep(1,10), rep(0.5,5), rep(0,8)), # tip c
    list(c(rep(0,5), rep(0.5, 5)), c(0, 0, 1, 1, 1), c(0.5, 1, rep(0, 6)))) # tip d

get_siteFChange_cherry(tree = tree, data = data)
```

>>>>

- `MeanSiteFChange_cherry(tree, data, index_islands, index_nonislands)`. The function computes the per-cherry frequency of sites with different methylation states at each structure (islands and non-islands) using \code{get_siteFChange_cherry}. 
Then it calculates the weighted mean site frequency of methylation changes for each cherry separately for islands and non-islands.

```{r}
# Set example tree and methylation data
tree <- "((a:1.5,b:1.5):2,(c:2,d:2):1.5);"
data <- list(
    list(rep(1,10), rep(0,5), rep(1,8)), # tip a
    list(rep(1,10), rep(0.5,5), rep(0,8)), # tip b
    list(rep(1,10), rep(0.5,5), rep(0,8)), # tip c
    list(c(rep(0,5), rep(0.5, 5)), c(0, 0, 1, 1, 1), c(0.5, 1, rep(0, 6)))) # tip d 
# Set the index for islands and non-island structures
index_islands <- c(2)
index_nonislands <- c(1, 3)

MeanSiteFChange_cherry(data = data, 
                       tree = tree, 
                       index_islands = index_islands, 
                       index_nonislands = index_nonislands)
```
